An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-03 tex/paper.tex
Adding a paragraph about the structure of the library.
Also, moving some of the examples to reuse.
Not sure if this fully gets what the reviewer wanted.

Further to these evolutionary ideas, \cite{Chellapilla1999, DavidB1993} are
examples of using machine learning techniques to evolve particular strategies.
In \cite{Axelrod}, Axelrod describes how similar techniques are used to
genetically evolve a high performing strategy from a given set of strategies.
Note that in his original work, Axelrod only used a base strategy set of 12
strategies for this evolutionary study. This is noteworthy as
\cite{Axelrod-Pythonprojectteam2015} now boasts over 120 strategies that are
readily available for a similar analysis.

@@

As stated in the \textbf{Introduction}, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

To date the library has had contributions from 24 contributors from a variety
of backgrounds which are not solely academic. These contributions have been in
terms of strategies. One strategy is the creation of an undergraduate
mathematics student with little prior knowledge of programming. Multiple other
strategies were written by a 15 year old secondary school student. Both of
these students are authors of this paper. As well as these strategy
contributions, vital architectural improvements to the library itself have also
been received.

You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}. Add:

\begin{itemize}
	\item Discuss match generators (possibly include in image?)
	\item Discuss what a strategy is (class, inheritance).
	\item Reuse (possibility of creating new tournament types).
\end{itemize}

@@

@@

\begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item Numpy 1.9.2:
        \item Matplotlib 1.4.2:
        \item Hypothesis  3.0:
        \item Testfixtures  4.9.1:
    \end{itemize}
\end{multicols}

>>>>

Further to these evolutionary ideas, \cite{Chellapilla1999, DavidB1993} are
examples of using machine learning techniques to evolve particular strategies.
In \cite{Axelrod}, Axelrod describes how similar techniques are used to
genetically evolve a high performing strategy from a given set of strategies.
Note that in his original work, Axelrod only used a base strategy set of 12
strategies for this evolutionary study. This is noteworthy as
\cite{Axelrod-Pythonprojectteam2015} now boasts over 135 strategies that are
readily available for a similar analysis.

@@

As stated in the \textbf{Introduction}, one of the main goals of the library is
to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). All components of the library are automatically tested using a
combination of unit, property and integration tests, these tests are run as new
features are added to the library to ensure compatibility. Thus, when submitting
a strategy, a simple test is required which ensures the strategy behaves as
expected.
Full contribution guidelines can be found in the documentation.  As an
example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source
code for the Grudger strategy as well as its corresponding test.

@@

You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}. This shows the parallel collection of strategies and
their tests. Furthermore the underlying engine for the library is a class for
tournaments which lives in the \texttt{tournament.py} module. This class is
responsible for coordinating the play of generated matches. This generation of
matches is the responsibility of a match generator class which is designed in
such a way as to be easily modifiable to create new types of matches. This is
described fuller in a tutorial in the documentation which shows how to easily
create a tournament where players only play each other with probability 0.5.
This will be discussed further in the reuse section of this paper.

@@

To date the library has had contributions from 25 contributors from a variety
of backgrounds which are not solely academic. These contributions have been in
terms of strategies. One strategy is the creation of an undergraduate
mathematics student with little prior knowledge of programming. Multiple other
strategies were written by a 15 year old secondary school student. Both of
these students are authors of this paper. As well as these strategy
contributions, vital architectural improvements to the library itself have also
been received.

@@

\begin{multicols}{2}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item Numpy 1.9.2
        \item Matplotlib 1.4.2
        \item Testfixtures 4.9.1
        \item Hypothesis 3.0 (only a requirement for development)
    \end{itemize}
\end{multicols}
